Predicting sales of newly published books

### 2015-11-03 paper.tex
Re-writing description of feature reduction techniques

Feature extraction is a ``transformation-based approach", therefore it transforms the original meaning of the features. This approach involves simplifying the amount of resources for accurately describing a large set of data, thus is employed when the semantics of the original dataset will not be needed by any future process. On the contrary, feature selection attempts to retain the meaning of the original feature set. It is part of what is called semantic-preserving techniques, known as ``selection-based approaches". By searching through all possible combinations of features, the aim of these techniques is to determine a minimal feature subset to reduce processing time, while obtaining the same or higher accuracy as the initial feature set \cite{liu1998feature}.

Thus, in order to reduce the dimensionality of the input data and to choose an 
appropriate set of variables, both the SOM \cite{kohonen1998} method and several 
feature selection methods have been applied.

@@

As far as the feature selection methods are concerned, both a correlation-based 
feature subset evaluation method (CfsSubsetEval) \cite{Hall1998} and an 
adaptation of relief for attribute estimation (ReliefFAttributeEval) evaluation 
method \cite{RobnikSikonja1997} are used with two search criteria: BestFirst, 
that searches the space of feature subsets by greedy hill-climbing augmented 
with a backtracking facility, and Ranker, that ranks features by their individual 
evaluations.

>>>>

Feature extraction is a ``transformation-based approach", therefore it transforms the original meaning of the features. This approach involves creating a subset of new features by combinations of the existing features, thus is employed when the semantics of the original dataset will not be needed by any future process. On the contrary, feature selection attempts to retain the meaning of the original feature set. It is part of what is called semantic-preserving techniques, known as ``selection-based approaches". By searching through all possible combinations of features, the aim of these techniques is to determine a minimal feature subset to reduce processing time, while obtaining the same or higher accuracy as the initial feature set \cite{liu1998feature}. In the problem this work assesses, it is very important to maintain the semantics of the set of initial variables, and therefore several feature selection methods have been applied.

In addition, in order to reduce the dimensionality of the input data and to choose an 
appropriate set of variables, the SOM \cite{kohonen1998} method has been also applied.

@@

As far as the feature selection methods are concerned, Weka separates the process in two parts:
\begin{itemize}
  \item Attribute evaluator: This is the method by which the feature subsets are assessed. In this work, both a correlation-based feature subset evaluation method (CfsSubsetEval) \cite{Hall1998} and an adaptation of relief for attribute estimation (ReliefFAttributeEval) evaluation method \cite{RobnikSikonja1997} are used. 
  \item Search method: This describes the structured way in which the set of possible feature subsets is studied, based on the results of the evaluator. Two search criteria have been used in this work: BestFirst, that searches the space of feature subsets by greedy hill-climbing augmented with a backtracking facility, and Ranker, that ranks features by their individual evaluations.
\end{itemize}
